Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador \newline \newline Combinando redes neuronales y geoestad\'{i}stica para evaluaci\'{o}n de deslizamientos de tierra del \'{a}rea Metropolitana de San Salvador, El Salvador

### 2015-10-22 paper.tex
22 Oct 2015 15:51

\bibitem{dewey}
Dewey J.W. White R.A., Hern\'{a}ndez D.A.
\newblock Seismicity and tectonics of El Salvador
\newblock \emph{Chapter 27 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 367-378. (2004)}

\bibitem{weber}
Weber H.S., Wiesemann G., Lorenz  W., Schmidt-Thom\'{e} M.
\newblock Mapa geol\'{o}gico de Republica de El Salvador
\newblock escala 1 : 100 000 (6 sheets).
\newblock \emph{ Bundesanstalt f\"ur Geowissenschaften und Rohstoffe, Hannover, Germany.
}
\penalty0 (1978).

\bibitem{bommer}
Bommer J.J., Rodriguez C.E.
\newblock Earthquake-induced landslides in Central Am\'{e}rica
\newblock \emph{Engineering Geology}.
(63):\penalty0 1889-220, (2002).

\bibitem{evans}
Evans S.G. Bent A.L.
\newblock Las Colinas landslide, Santa Tecla:  A higly destructive flowslide triggered by January 13, 2001, El Salvador earthquake.
\newblock \emph{Chapter 3 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 25-37. (2004)}

\bibitem{jibson}
Jibson R.W., Crone A.J., Harp E.L., Baum R.L., Major J.J., Pullinguer C.R., Escobar D., Martinez M., Smith M.E. 
\newblock Landslides triggered by the 13 January and 13 February 2001, earthquakes.
\newblock \emph{ Chapter 6 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J. 69-88. (2004)}

\bibitem{crone}
Crone A.J., Baum R.L., Lidke D.J., Sather D.N.D., Bradley L.-A., Tarr A.C.
\newblock Landslides Induced by Hurricane Mitch in El Salvador-An Inventory and Description of Selected Features
\newblock \emph{USGS Open File Repord 01-444. (2002)}

\bibitem{Carrara1983403}
Alberto Carrara.
\newblock Multivariate models for landslide hazard evaluation.
\newblock \emph{Journal of the International Association for Mathematical
  Geology.}, 15\penalty0 (3):\penalty0 403--426, 1983.
\newblock ISSN 0020-5958.

\bibitem{hessd-10-12643-2013}
G.~Capparelli and P.~P.~Versace.
\newblock Landslide susceptibility from mathematical model in sarno area.
\newblock \emph{Hydrology and Earth System Sciences Discussions}, 10\penalty0
  (10):\penalty0 12643--12662, 2013.

\bibitem{doi:10.1080/19475705.2010.498151}
Biswajeet Pradhan, Hyun-Joo Oh, and Manfred Buchroithner.
\newblock Weights-of-evidence model applied to landslide susceptibility mapping
  in a tropical hilly area.
\newblock \emph{Geomatics, Natural Hazards and Risk}, 1\penalty0 (3):\penalty0
  199--223, 2010.

\bibitem{Neu2012511}
Bettina Neuh\"auser, Bodo Damm, and Birgit Terhorst.
\newblock Gis-based assessment of landslide susceptibility on the base of the
  weights-of-evidence model.
\newblock \emph{Landslides}, 9\penalty0 (4):\penalty0 511--528, 2012.
\newblock ISSN 1612-510X.

\bibitem{Bern198839}
Campbell R.H. Brookshire~D.S. Bernknopf, R.L. and C.D Shapiro.
\newblock A probabilistic approach to landslide hazard mapping in cincinnati,
  ohio, with application for economic evaluation.
\newblock \emph{Bulletin of the Association of Engineering Geologists},
  XXV\penalty0 (1):\penalty0 39--56, 1988.

\bibitem{Chung2003451}
Chang-JoF. Chung and AndreaG. Fabbri.
\newblock Validation of spatial prediction models for landslide hazard mapping.
\newblock \emph{Natural Hazards}, 30\penalty0 (3):\penalty0 451--472, 2003.
\newblock ISSN 0921-030X.
\newblock doi:{10.1023/B:NHAZ.0000007172.62651.2b}.

\bibitem{doi:10.1080/01431160310001618734}
S.~Lee, J.~Choi, and K.~Min.
\newblock Probabilistic landslide hazard mapping using gis and remote sensing
  data at boun, korea.
\newblock \emph{International Journal of Remote Sensing}, 25\penalty0
  (11):\penalty0 2037--2052, 2004.

\bibitem{akgun2012}
Akgun, Aykut
\newblock A comparison of landslide susceptibility maps produced by logistic regression, multi criteria decision, and likelihood ratio methods: a case study at Izmir, Turkey
\newblock \emph{Landslides},
  (11):\penalty0 9, 1, 93--106, 2012.
\newblock Springer.

\bibitem{gaskill}
Gaskill, Jacob and Zuber, Brian and Nordman, Erik
\newblock Analyzing Landslide Susceptibility in St. Vincent and the Grenadines Using Co-Kriging and Logistic Regression
\newblock \emph{The 2015 IMAGIN Award, Michigan United States}.

\bibitem{garcia2008}
Garc\'{i}a-Rodr\'{i}guez M.J., Malpica J.A., Benito B., D\'{i}az M.
\newblock  Susceptibility assessment of earthquake-triggered landslides in El Salvador using logistic regression.
\newblock \emph{Geomorphology}
\penalty0 95, 172-191, 2008.

\bibitem{garcia2010}
Garc\'{i}a-Rodr\'{i}guez M.J., Malpica J.A.
\newblock Assessment of earthquake-triggered landslide susceptibility in El Salvador based on an Artificial Neural Network model.
\newblock \emph{Nat. Hazards Earth Syst. Sci.}
\penalty0 10, 1307–1315, 2010. 
\newblock doi:10.5194/nhess-10-1307-2010.

\bibitem{Melchiorre2011410}
C.~Melchiorre, E.A.~Castellanos Abella, C.J. van Westen, and M.~Matteucci.
\newblock Evaluation of prediction capability, robustness, and sensitivity in
  non-linear landslide susceptibility models, guant\'{a}namo, cuba.
\newblock \emph{Computers {\&} Geosciences}, 37\penalty0 (4):\penalty0 410 --
  425, 2011.
\newblock ISSN 0098-3004.

\bibitem{Zeng2001374}
Xu~Zeng-wang.
\newblock Gis and ann model for landslide susceptibility mapping.
\newblock \emph{Journal of Geographical Sciences}, 11\penalty0 (3):\penalty0
  374--381, 2001.
\newblock ISSN 1009-637X.
\newblock doi:{10.1007/BF02892323}.

\bibitem{Ermini2005327}
Artificial neural networks applied to landslide susceptibility assessment.
\newblock \emph{Geomorphology}, 66\penalty0 (1–4):\penalty0 327 -- 343, 2005.
\newblock ISSN 0169-555X
\newblock doi:10.1016/j.geomorph.2004.09.025.

\bibitem{Yesilnacar2005251}
E. Yesilnacar and T. Topal.
\newblock Landslide susceptibility mapping: A comparison of logistic regression and neural networks methods in a medium scale study, Hendek region (Turkey).
\newblock \emph{Engineering Geology}, 79\penalty0
  (11):\penalty0 251-266, 2005.
\newblock ISSN 0013-7952,
\newblock doi:10.1080/01431160310001618734.

\bibitem{ballabio2012support}
Ballabio, Cristiano and Sterlacchini, Simone
\newblock Support vector machines for landslide susceptibility mapping: the Staffora River Basin case study, Italy
\newblock \emph{Mathematical geosciences},
  (11):\penalty0 1, 47--70, 2012.
\newblock Springer.

\bibitem{tien2012landslide}
Tien Bui, Dieu and Pradhan, Biswajeet and Lofman, Owe and Revhaug, Inge
\newblock Landslide susceptibility assessment in vietnam using support vector machines, decision tree, and Naive Bayes Models
\newblock \emph{Mathematical Problems in Engineering},
  (11):\penalty0 2012, 2012.
\newblock Hindawi Publishing Corporation.

\bibitem{van2006landslide}
Van Westen, CJ and Van Asch, Th WJ and Soeters, R
\newblock Landslide hazard and risk zonation why is it still so difficult?
\newblock \emph{Bulletin of Engineering geology and the Environment}.
(65):\penalty0 2, 167--184, 2006
\newblock Springer.

\bibitem{minecon}
Ministerio de Economia- Direcci\'{o}n General de Estad\'{i}stica y Censos
\newblock VI Censo de Poblaci\'{o}n y V de Vivienda
\newblock \emph{2007-2008}.
\penalty0 Available from http://goo.gl/yvjzPy

\bibitem{schmidt1975}
Schmidt-Thom\'{e} M.
\newblock The geology in San Salvador area (El Salvador, Central America), a basis for city development and planning.
\newblock \emph{Geol. Jb.}.
\penalty0 13, 207-228, 1975.

\bibitem{chavez2014a}
Ch\'{a}vez J.A., Sebesta J., Kopecky L., L\'{o}pez R.
\newblock Application of Geomorphologic Knowledge for Erosion Hazard Mapping
\newblock \emph{Natural Hazards}.
\penalty0 71,1323–1354, 2014.
\newblock doi:10.1007/s11069-013-0948-8.

\bibitem{hernan2004}
Hern\'{a}ndez W.E.
\newblock Caracter\'{i}sticas Geomec\'{a}nicas y Vulcanologicas de las Tefras Tierra Blanca Joven, Caldera de Ilopango, El Salvador.
\newblock MSc Thesis. Universidad Polit\'{e}cnica de Madrid – Universidad Polit\'{e}cnica de El Salvador.
\penalty0 2004

\bibitem{chavez2014b}
Ch\'{a}vez J.A.,  Landaverde J.M., Ayala O.E., Mendoza L.E. (2014b). 
\newblock Application of Constitutive Models in the Volcanic Tephra ``Tierra Blanca Joven''.
\newblock \emph{Ingenier\'{i}a.}
\penalty0  24 (2).53-78.
\newblock  ISSN: 2215-2652.

\bibitem{rolo2004}
Rolo R., Bommer J.J., Houghton B.F., Vallance J.W., Berdousis P., Mavrommati C., Morphy W.
\newblock Geologic and engineering characterization of Tierra Blanca pyroclastic ash deposits.
\newblock \emph{Chapter 5 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
\penalty0  55-67, 2004.

\bibitem{rymer1987}
Rymer M.J. 
\newblock The San Salvador Earthquake of October 10, 1986.
\newblock \emph{Geologic Aspects Earthquake Spectra.}
\penalty0 3(3), 435-463, 1987.

\bibitem{dull2004}
Dull R.A.
\newblock Lessons from the mud, lessons from the Maya: Paleoecological records of the Tierra Blanca Joven eruption.
\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
\penalty0 237-244., 2004.

\bibitem{major2004}
Major J.J. Chilling S.P., Pullinguer C.R., Escobar C.D.
\newblock Debris-flow hazards at San Salvador, San Vicente, and San Miguel volcanoes, El Salvador.
\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
\penalty0 89-108, 2004.

\bibitem{sofield2004}
Sofield D.
\newblock Eruptive history and volcanic hazards of Volcan San Salvador. 
\newblock \emph{Chapter 7 in Geological Society of America Special paper 375 in Natural Hazards in El Salvador of Rose W.I., Bommer J.J., L\'{o}pez D.L., Carr M.J. and Major J.J.}
\penalty0 147-158, 2004.

\bibitem{beni2012}
Benito M.B., Lindholm C., Camacho E., Climent \'{A}., Marroqu\'{i}n G., Molina E.,Rojas W., Escobar J.J., Talavera E., Alvarado G.E. and Torres Y.
\newblock A New Evaluation of Seismic Hazard for the Central America Region. 
\newblock \emph{Bulletin of the Seismological Society of America}
\penalty0 102 (2), 504-523. 2012.
\newblock  doi: 10.788/0120110015

\bibitem{FAQANN}
Warren S. Sarle
\newblock  [cited 2014 January 10]. Available from http://goo.gl/k8fKhM

\bibitem{McNelis2005}
Paul D. McNelis
\newblock Estimation of a Network with Evolutionary Computation
\newblock \emph{Academic Press},
  (11):\penalty0 59-84, 2005.
\newblock ISBN 9780124859678,
\newblock doi:10.1016/B978-012485967-8.50003-8.

\bibitem{rproject}
R Core Team
\newblock R: A Language and Environment for Statistical Computing.
\newblock \emph{R Foundation for Statistical Computing.}
\penalty0 Vienna, Austria, 2014.

\bibitem{bivand2008applied}
Bivand, Roger S and Pebesma, Edzer J and G{\'o}mez-Rubio, Virgilio and Pebesma, Edzer Jan
\newblock Applied spatial data analysis with R
\newblock \emph{volume 747248717}
\penalty0 Springer, 2014.

\bibitem{nicolas2015}
Nicolas Christou.
\newblock Ordinary kriging in terms of the covariance function
\newblock \emph{University of California, Los Angeles}
\penalty0 [cited 2015 June 04]. Available from http://goo.gl/0J1RkO

\bibitem{fernan2008}
Fernandez-Lavado C., Sanchez A., Amenos M., Barrio J.
\newblock Caracterizaci\'{o}n de la susceptibilidad y de la amenaza por movimientos de ladera del \'{A}rea Metropolitana de San Salvador (AMSS). Scale 1: 75000 (1 Sheet).
\newblock \emph{Project IPGARAMSS framework. Ge\'{o}logos del Mundo. San Salvador, El Salvador.}
\penalty0 2008.

\bibitem{snet2004}
SNET-MARN, Servicio Nacional de Estudios Territoriales-Ministerio de Ambiente y Recursos Naturales
\newblock Memoria T\'{e}cnica Para El Mapa De Susceptibilidad de Deslizamientos de Tierra En El Salvador.
\newblock \emph{Ministerio de Ambiente y Recursos Naturales}
\penalty0 [cited 2015 June 04]. Map available from http://www.snet.gob.sv/ver/geologia/susceptibilidad+actual/

\bibitem{aki1993}
Aki, K. 
\newblock Local site effects on weak and strong ground motion. In F. Lund (ed.) New Horizons in Strong Motion: Seismic Studies and Engineering Practice.
\newblock \emph{Tectonophysics}
\penalty0 218, 93-111, 1993.

\bibitem{crosta2005}
Crosta G.B., Imposimato S., Rodderman, Chiesa S.m, Moia F. 
\newblock Small fast-moving flow-like landslides in volcanic deposits: The 2001 Las Colinas Landslide (El Salvador). 
\newblock \emph{Engineering Geology.}
\penalty0 79, 185-214, 2005.

>>>>

\bibitem{dewey} 
Dewey, J.W.; White, R.A.: Hern\'{a}ndez, D.A. (2004)
``Seismicity and tectonics of El Salvador",
{\it Geological Society of America Special Papers} {\bf 375}: 367--378.

\bibitem{weber}  
Weber, H.S.; Wiesemann, G.; Lorenz, W.: Schmidt-Thom\'{e}, M. (1978)
``Mapa geol\'{o}gico de la Republica de El Salvador'',
Preprint, Bundesanstalt f\"ur Geowissenschaften und Rohstoffe, Hannover, Germany.

\bibitem{bommer}
Bommer, J.J.: Rodriguez, C.E. (2002)
``Earthquake-induced landslides in Central Am\'{e}rica", 
{\it Engineering Geology} {\bf 63}(3): 189--220.

\bibitem{evans}  
Evans, S.G: Bent, A.L. (2004) 
``Las Colinas landslide, Santa Tecla:  A higly destructive flowslide triggered by January 13, 2001, El Salvador earthquake", 
{\it Geological Society of America Special Papers} {\bf 375}: 25--37.

\bibitem{jibson}  
Jibson, R.W.; Crone, A.J.; Harp, E.L.; Baum, R.L.; Major, J.J.; Pullinguer, C.R.; Escobar, D.; Martinez, M: Smith, M.E. (2004) 
``Landslides triggered by the 13 January and 13 February 2001, earthquakes", 
{\it Geological Society of America Special Papers} {\bf 375}: 69--88.

\bibitem{crone}  
Crone, A.J.; Baum, R.L.; Lidke, D.J.; Sather, D.N.D.; Bradley, L.A.: Tarr, A.C. (2002)
``Landslides Induced by Hurricane Mitch in El Salvador-An Inventory and Description of Selected Features'',
Preprint, USGS Open File Report 01-444.

\bibitem{Carrara1983403} 
Carrara, A. (1983) 
``Multivariate models for landslide hazard evaluation", 
{\it Journal of the International Association for Mathematical
  Geology} {\bf 15}(3): 403--426.

\bibitem{hessd-10-12643-2013}  
Capparelli, G.: Versace, P.P. (2013)
``Landslide susceptibility from mathematical model in sarno area", 
{\it Hydrology and Earth System Sciences Discussions} {\bf 10}(10): 12643--12662.

\bibitem{doi:10.1080/19475705.2010.498151}  
Pradhan, B.; Oh, H.: Buchroithner, M. (2010)
``Weights-of-evidence model applied to landslide susceptibility mapping
  in a tropical hilly area", 
{\it Geomatics, Natural Hazards and Risk} {\bf 1}(3): 199--223.

\bibitem{Neu2012511} 
Neuh\"auser, B.; Damm, B.: Terhorst, B. (2012)
``Gis-based assessment of landslide susceptibility on the base of the
  weights-of-evidence model", 
{\it Landslides} {\bf 9}(4): 511--528.

\bibitem{Bern198839} 
Campbell, R.H.; Brookshire, D.S.; Bernknopf, R.L.: Shapiro, C.D. (1988)
``A probabilistic approach to landslide hazard mapping in cincinnati,
  ohio, with application for economic evaluation", 
{\it Bulletin of the Association of Engineering Geologists} {\bf 25}(1): 39--56.

\bibitem{Chung2003451}  
Chung, C.J.F.: Fabbri, A. G. (2003).
``Validation of spatial prediction models for landslide hazard mapping", 
{\it Natural Hazards} {\bf 30}(3): 451--472.

\bibitem{doi:10.1080/01431160310001618734} 
Lee, S.; Choi, J.: Min, K. (2004)
``Probabilistic landslide hazard mapping using gis and remote sensing
  data at boun, korea", 
{\it International Journal of Remote Sensing} {\bf 25}(11): 2037--2052.

\bibitem{akgun2012}  
Akgun, A. (2012) 
``A comparison of landslide susceptibility maps produced by logistic regression, multi criteria decision, and likelihood ratio methods: a case study at Izmir, Turkey", 
{\it Landslides} {\bf 9}(1): 93--106.

\bibitem{gaskill} 
Gaskill, J.; Zuber, B.: Nordman, E. (2015)
``Analyzing Landslide Susceptibility in St. Vincent and the Grenadines Using Co-Kriging and Logistic Regression'', 
Preprint, The 2015 IMAGIN Award, Michigan United States.

\bibitem{garcia2008} 
Garc\'{i}a-Rodr\'{i}guez, M.J.; Malpica, J.A.; Benito, B.: D\'{i}az, M. (2008) 
``Susceptibility assessment of earthquake-triggered landslides in El Salvador using logistic regression", 
{\it Geomorphology} {\bf 95}(3): 172-191.

\bibitem{garcia2010} 
Garc\'{i}a-Rodr\'{i}guez, M.J.: Malpica, J.A. (2010)
``Assessment of earthquake-triggered landslide susceptibility in El Salvador based on an Artificial Neural Network model", 
{\it Natural Hazards and Earth System Science} {\bf 10}(6): 1307–1315.

\bibitem{Melchiorre2011410}  
Melchiorre, C.; Abella, E. C.; van Westen, C. J.: Matteucci, M. (2011)
``Evaluation of prediction capability, robustness, and sensitivity in
  non-linear landslide susceptibility models, guant\'{a}namo, cuba", 
{\it Computers {\&} Geosciences} {\bf 37}(4): 410--425.

\bibitem{Zeng2001374}  
Zeng-wang, X. U. (2001).
``Gis and ann model for landslide susceptibility mapping", 
{\it Journal of Geographical Sciences} {\bf 11}(3): 374--381.

\bibitem{Ermini2005327} 
Ermini, L.; Catani, F.: Casagli, N. (2005). 
``Artificial neural networks applied to landslide susceptibility assessment", 
{\it Geomorphology} {\bf 66}(1): 327--343.

\bibitem{Yesilnacar2005251} 
Yesilnacar, E.: Topal, T. (2005)
``Landslide susceptibility mapping: A comparison of logistic regression and neural networks methods in a medium scale study, Hendek region (Turkey)", 
{\it Engineering Geology} {\bf 79}(3): 251-266.

\bibitem{ballabio2012support}  
Ballabio, C.: Sterlacchini, S. (2012) 
``Support vector machines for landslide susceptibility mapping: the Staffora River Basin case study, Italy", 
{\it Mathematical geosciences} {\bf 44}(1): 47--70.

\bibitem{tien2012landslide} 
Tien Bui, D.; Pradhan, B.; Lofman, O.: Revhaug, I. (2012)
``Landslide susceptibility assessment in vietnam using support vector machines, decision tree, and Naive Bayes Models", 
{\it Mathematical Problems in Engineering} {\bf 2012}.

\bibitem{van2006landslide}  
Van Westen, C. J.; Van Asch, T. W.: Soeters, R. (2006).
``Landslide hazard and risk zonation why is it still so difficult?", 
{\it Bulletin of Engineering geology and the Environment} {\bf 65}(2): 167--184.

\bibitem{minecon}  
Ministerio de Economia- Direcci\'{o}n General de Estad\'{i}stica y Censos. (2013) 
``VI Censo de Poblaci\'{o}n y V de Vivienda'',
in:\\ {\tt http://goo.gl/yvjzPy},\\
consulted 23-Dec-2013, 2:30 p.m.

\bibitem{schmidt1975} 
Schmidt-Thom\'{e} M. (1975)
``The geology in the San Salvador area (El Salvador, Central America), a basis for city development and planning'',
Preprint,  Schweizerbart'sche Verlagsbuchhandlung.

\bibitem{chavez2014a} 
Ch\'{a}vez, J.A.; Sebesta, J.; Kopecky, L.: L\'{o}pez, R. (2014)
``Application of Geomorphologic Knowledge for Erosion Hazard Mapping", 
{\it Natural Hazards} {\bf 71}(3): 1323–1354.

\bibitem{hernan2004} 
Hern\'{a}ndez, W.E. (2004)
{\it Caracter\'{i}sticas Geomec\'{a}nicas y Vulcanologicas de las Tefras Tierra Blanca Joven, Caldera de Ilopango, El Salvador}.
MSc Thesis. Universidad Polit\'{e}cnica de Madrid – Universidad Polit\'{e}cnica de El Salvador.

\bibitem{chavez2014b} 
Ch\'{a}vez J.A.; Landaverde J.M.; Ayala O.E.: Mendoza L.E. (2014). 
``Application of Constitutive Models in the Volcanic Tephra ``Tierra Blanca Joven''", 
{\it Ingenier\'{i}a} {\bf 24}(2): 53-78.

\bibitem{rolo2004} 
Rolo, R.; Bommer, J.J.; Houghton, B.F.; Vallance, J.W.; Berdousis, P.; Mavrommati, C.: Morphy, W. (2004)
``Geologic and engineering characterization of Tierra Blanca pyroclastic ash deposits", 
{\it Geological Society of America Special Papers} {\bf 375}: 55--68.

\bibitem{rymer1987}  
Rymer, M.J. (1987) 
``The San Salvador Earthquake of October 10, 1986-Geologic Aspects", 
{\it Earthquake Spectra} {\bf 3}(3): 435-463.

\bibitem{dull2004}  
Dull, R.A. (2004)
``Lessons from the mud, lessons from the Maya: Paleoecological records of the Tierra Blanca Joven eruption", 
{\it Geological Society of America Special Papers} {\bf 375}: 237--244.

\bibitem{major2004} 
Major, J.J.; Chilling, S.P.; Pullinguer, C.R.: Escobar, C.D. (2004)
``Debris-flow hazards at San Salvador, San Vicente, and San Miguel volcanoes, El Salvador", 
{\it Geological Society of America Special Papers} {\bf 375}: 89--108.

\bibitem{sofield2004}  
Sofield, D. (2004)
``Eruptive history and volcanic hazards of Volcan San Salvador", 
{\it Geological Society of America Special Papers} {\bf 375}: 147--158.

\bibitem{beni2012}
Benito, M.B.; Lindholm, C.; Camacho, E.; Climent, \'{A}.; Marroqu\'{i}n, G.; Molina, E.; Rojas, W.; Escobar, J.J.; Talavera, E.; Alvarado, G.E.: Torres, Y. (2012)
``A New Evaluation of Seismic Hazard for the Central America Region", 
{\it Bulletin of the Seismological Society of America} {\bf 102}(2): 504--523.

\bibitem{FAQANN}
Warren, S. (2002) 
``Neural Network FAQ'',
in:\\ {\tt ftp://ftp.sas.com/pub/neural/FAQ.html},\\
consulted 10-Jan-2014, 10:30 a.m.

\bibitem{McNelis2005}
McNelis, P.D. (2005)
{\it Estimation of a Network with Evolutionary Computation}. 
Academic Press.

\bibitem{rproject}
R Core Team. (2014)
{\it R: A Language and Environment for Statistical Computing}. 
Vienna: R Foundation for Statistical Computing.

\bibitem{bivand2008applied}
Bivand, R.S.; Pebesma, E.J.; Gomez-Rubio, V.: Pebesma, E.J. (2008)
{\it Applied spatial data analysis with R}. 
New York: Springer.

\bibitem{nicolas2015}
Christou, N. (2013)
``Ordinary kriging in terms of the covariance function'',
in:\\ {\tt http://goo.gl/0J1RkO},\\
consulted 23-Jun-2013, 5:30 p.m.

\bibitem{fernan2008}
Fernandez-Lavado, C.; Sanchez, A.; Amenos, M.: Barrio, J. (2008)
``Caracterizaci\'{o}n de la susceptibilidad y de la amenaza por movimientos de ladera del \'{A}rea Metropolitana de San Salvador (AMSS). Scale 1: 75000 (1 Sheet)'',
Preprint, Project IPGARAMSS framework. Ge\'{o}logos del Mundo. San Salvador, El Salvador.

\bibitem{snet2004}
SNET-MARN, Servicio Nacional de Estudios Territoriales-Ministerio de Ambiente y Recursos Naturales. (2013) 
``Memoria T\'{e}cnica Para El Mapa De Susceptibilidad de Deslizamientos de Tierra En El Salvador'',
in:\\ {\tt http://www.snet.gob.sv/ver/geologia/susceptibilidad+actual/},\\
consulted 12-Sep-2013, 2:30 p.m.

\bibitem{aki1993}
Aki, K. (1993) 
``Local site effects on weak and strong ground motion. In F. Lund (ed.) New Horizons in Strong Motion: Seismic Studies and Engineering Practice", 
{\it Tectonophysics} {\bf 218}(1): 93--111.

\bibitem{crosta2005}
Crosta, G. B.; Imposimato, S.; Roddeman, D.; Chiesa, S.: Moia, F. (2005)
``Small fast-moving flow-like landslides in volcanic deposits: the 2001 Las Colinas Landslide (El Salvador)", 
{\it Engineering geology} {\bf 79}(3): 185--214.
